---
title: "Twitter Ukraine"
author: "Joty Sekhon"
date: "07/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rtweet)
library (knitr)

```

## Data import

#collect tweets about coffee

```{r}

ukraine_tweets<-search_tweets(
  q="ukraine",
  n=35,
  include_rts = FALSE,
  lang="en",
  retryonratelimit = TRUE
)

```

Cleaner version:

```{r}
#look at first 6 obs
ukraine_tweets%>%
  head()

#look at structure
ukraine_tweets%>%
  str()

  
ukraine_short<-ukraine_tweets%>%
  select(user_id, screen_name, created_at, text, favourites_count, retweet_count)

ukraine_short%>%write_csv("ukraine_7_05_2022.csv")
ukraine_tweets<-read_csv("ukraine_7_05_2022.csv")

```

### Explore frequency of tweets


```{r}
ts_plot(ukraine_tweets, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets with ukraine",
       subtitle = paste0(format(min(ukraine_tweets$created_at), "%d %B %Y"), " to ", format(max(ukraine_tweets$created_at),"%d %B %Y")),
       caption = "Ukraine tweets Data collected from Twitter") +
  theme_minimal()
```

### Top tweeting location
Most Twitter users turn off their location in their privacy settings but those that don’t add valuable location information to their tweets. We can count unique values of the “place_full_name” variable to obtain the most frequent tweet location for the search term ukraine.


```{r}
ukraine_tweets %>% 
  filter(!is.na(place_full_name)) %>% 
  count(place_full_name, sort = TRUE) %>% 
  top_n(10)
```


### Most retweeted tweet

#`retweet_count` variable shows retweeting. We sort all the tweets in descending order by the size of the “retweet_count”, top_n the first 20 rows and print the date, handle, text and retweet count.

```{r}
ukraine_tweets %>% 
  arrange(-retweet_count) %>%
  top_n(20, retweet_count) %>% 
  select(created_at, screen_name, text, retweet_count)
```

# Part 2

``` {r}
# Present the first 10 tweets from your dataset using kable()
ukraine_tweets %>%
  head(10) %>%
  kable()
```

```{r}
# Visualise the frequency of your tweets 
ts_plot(ukraine_tweets, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets with Ukraine",
       subtitle = paste0(format(min(ukraine_tweets$created_at), "%d %B %Y"), "to",
                         format(max(ukraine_tweets$created_at), "%d %B %Y")),
       caption = "Data collected on search term ukraine from Twitter's REST API via rtweet") +
  theme_minimal()
```

``` {r}
# Identify top tweeting locations and present the first 10
ukraine_tweets %>% 
  filter(!is.na(place_full_name)) %>% 
  count(place_full_name, sort = TRUE) %>% 
  top_n(10)%>%
  kable()
# Identifies the most popular location tweeting about ukraine on the date the dataset was created.
```

``` {r}
#Identify the most retweeted tweets and present top 20
ukraine_tweets %>% 
  arrange(-retweet_count) %>%
  top_n(20, retweet_count) %>% 
  select(created_at, screen_name, text, retweet_count) %>%
  kable()

# This looks at the top 20 search terms with ukraine in it from the date the search was commenced on 06-05-2022.
# It includes the screen name of the tweeter and the retweet count in descending order and the twitter text the user posted.
```

``` {r}
# Identify the most liked tweets and present the first 15.
ukraine_tweets %>% 
  arrange(-favourites_count) %>%
  top_n(15, favourites_count) %>% 
  select(created_at, screen_name, text, favourites_count) %>%
  kable()

# Takes the top 15 tweets from the created dataset and shows it in descending order.
# Shows which tweets gained the most likes on the day the dataset was created 06/05/2022.
```

``` {r}
# Identify top tweeters in your dataset and present the first 5
ukraine_tweets %>% 
  count(screen_name, sort = TRUE) %>%
  top_n(5) %>%
  mutate(screen_name = paste0("@", screen_name)) %>%
  kable()
# This shows us the top 5 tweeters in our created dataset
# To identify the most active tweeters we use the “screen_name” variable to tot up the number of tweets by Twitter handle. Than can then add back the @ symbol using the paste0() function.
```

``` {r}
# Identify top emojis in your dataset and present the first 10
install.packages("devtools")
library(devtools)
devtools::install_github("hadley/emo")
library(emo)
ukraine_tweets %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  top_n(10) %>%
  kable()
##To identify the most frequent top 10 emoji we use ji_extract_all() function from the emo package
#This function extracts all the tweets emojis
#Than using the unnest() function from the tidyr package to split the emojis from its package and sort in desc order
```

```{r}
# Identify top hashtags in your dataset and present the first 10
library(tidytext)
ukraine_tweets %>% 
  unnest_tokens(hashtag, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(hashtag, "^#"),
        hashtag != "#ClimateEmergency") %>%
  count(hashtag, sort = TRUE) %>%
  top_n(10) %>%
  kable()

# To get the top 10 hashtags we must convert the text into 1 word per row using the unnest_tokens() to format
# Than select the top 10 hashtags after the have been counted and view them in descending order
```

```{r}
# Identify top mentions in your dataset and present the first 10
ukraine_tweets %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  top_n(10) %>%
  kable()

#Here what we will do is tokenise the text of every tweet and than use the function `str_detect()` from the package `tidyverse` to filter out words that start with an @ .
```

``` {r}
# Get a list of all accounts that the top tweeter follows and present the first 5
get_friends(
  "TheAnswerYes",
  n = 5) %>%
  kable()
```


``` {r}
# Get a list of followers of the top tweeter and present the first 5 
get_followers(
  "TheAnswerYes",
  n = 5) %>%
  kable()
```


